Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-25 WRITEUP/ms.tex

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_2.0}.pdf}
\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.pdf}
\caption{
Toomre $Q$ maps derived from the central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower. The contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown separately in the left and middle panels, respectively. Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
%A divergent colormap is used for the Toomre $Q$ maps to facilitate identification of regions above and below $\log{Q}$\eq0.
Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} of \flower indicates that the stellar component plays an important role in governing the stability of the MCCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts. \AP{maybe it is better to put a single set of maps, with FOV from -1.5 to 1.5 kpc}
\label{fig:Qeff}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
\caption{
Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower. Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively. The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
%A divergent colormap is used for the Toomre $Q$ maps to facilitate identification of regions above and below $\log{Q}$\eq0.
Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} 
reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations 
in relatively evolved and enriched systems at high redshifts. 
\label{fig:Qeff}}
\end{figure*}
